A simplified dynamic bioenergetic model for coral-*Symbiodinium* symbioses

### 2016-09-26 JTB_ms/JTB_ms.Rmd
change parameter jNPQ to kNPQ

| Symbol  | Description                            | Value  | Units              |
| ------- | -------------------------------------- | ------ | ------------------ |
| $n_{NH}$ | N:C molar ratio in host biomass | 0.19 | -- |
| $n_{NS}$ | N:C molar ratio in symbiont biomass | 0.2 | -- |
| $n_{NX}$ | N:C molar ratio in prey biomass | 0.13 | -- |
| $j_{HT}^0$ | Specific turnover rate of host biomass | 0.03 | d^-1^ |
| $j_{ST}^0$ | Specific turnover rate of symbiont biomass | 0.03 | d^-1^ |
| $\sigma_{NH}$ | Proportion host nitrogen turnover recycled | 0.9 | -- |
| $\sigma_{CH}$ | Proportion host carbon turnover recycled | 0.9 | -- |
| $\sigma_{NS}$ | Proportion symbiont nitrogen turnover recycled | 0.9 | -- |
| $\sigma_{CS}$ | Proportion symbiont carbon turnover recycled | 0.9 | -- |
| $j_{Xm}$ | Maximum specific feeding rate of host | 0.1292 | molX CmolH^-1^ d^-1^ |
| $K_X$ | Half-saturation constant for prey uptake by host | 20e-6 | molX L^-1^ | 
| $j_{Nm}$ | Maximum specific DIN uptake rate by host | 0.048 | molN CmolH^-1^ d^-1^ |
| $K_N$ | Half-saturation constant for DIN uptake by host | 0.46e-6 | molN L^-1^ | 
| $j_{CO_2}^p$ | Passive CO~2~ delivery to symbiont | 4.04e-3 | molC CmolH^-1^ d^-1^ |
| $j_{CO_2}^a$ | Active CO~2~ delivery to symbiont | 0.32--18.0 | molC CmolH^-1^ d^-1^ |
| $j_{HGm}$ | Maximum specific growth rate of host | 1 | d^-1^ |
| $n_{LC}$ | Quantum yield of photosynthesis | 0.1 | molC mol ph^-1^ |
| $\bar{a}^*$ | Effective light-absorbing cross-section of symbiont | 1.34 | m^2^ CmolS^-1^ |
| $j_{NPQ}$ | Non-photochemical quenching capacity of symbiont | 40 | mol ph CmolS^-1^ d^-1^ |
| $k_{ROS}$ | Excess photon energy that doubles ROS prod. | 40-80 | mol ph CmolS^-1^ d^-1^ |
| $k$ | Exponent on ROS production rate | 1 | -- |
| $j_{CPm}$ | Maximum specific photosynthesis rate of symbiont | 2.8 | molC CmolS^-1^ d^-1^ |
| $j_{SGm}$ | Maximum specific growth rate of symbiont | 0.25 | d^-1^ |

@@

This excess light energy must be quenched by alternative pathways in order to prevent photo-oxidative damage. *Symbiodinium* may utilize a variety of pathways for non-photochemical quenching [NPQ; @Roth:2014wf], which we collect in a total capacity for NPQ as a parameter of the symbiont ($j_{NPQ}$). If light energy exceeds the total capacity of both carbon fixation and NPQ, then damaging reactive oxygen species (ROS) may be produced. We represent this as a scaled flux of ROS $c_{ROS}$, which takes a value of 1 when all light absorbed is quenched by photochemistry and NPQ, and increases as the amount of excess excitation energy increases.

@@

where $j_{NPQ}$, $k_{ROS}$, and $k$ are parameters of the symbiont that determine the onset and rate of ROS production. Importantly, $c_{ROS}$ as specified here is not a function of absolute light absorption, but rather the amount of excess light energy $j_{eL}$ after accounting for carbon fixation and NPQ. A direct consequence of this formulation is that carbon-limitation of photosynthesis can lead to photo-oxidative stress, a mechanism of biological importance [@Wooldridge:2009p7807] that was not captured by previous representations of photo-oxidative stress [@Eynaud:2011tv]. Moreover, this formulation allows functional diversity among symbiont types to be explored by changing the parameters $j_{NPQ}$, $k_{ROS}$, and $k$.

>>>>

| Symbol  | Description                            | Value  | Units              |
| ------- | -------------------------------------- | ------ | ------------------ |
| $n_{NH}$ | N:C molar ratio in host biomass | 0.19 | -- |
| $n_{NS}$ | N:C molar ratio in symbiont biomass | 0.2 | -- |
| $n_{NX}$ | N:C molar ratio in prey biomass | 0.13 | -- |
| $j_{HT}^0$ | Specific turnover rate of host biomass | 0.03 | d^-1^ |
| $j_{ST}^0$ | Specific turnover rate of symbiont biomass | 0.03 | d^-1^ |
| $\sigma_{NH}$ | Proportion host nitrogen turnover recycled | 0.9 | -- |
| $\sigma_{CH}$ | Proportion host carbon turnover recycled | 0.9 | -- |
| $\sigma_{NS}$ | Proportion symbiont nitrogen turnover recycled | 0.9 | -- |
| $\sigma_{CS}$ | Proportion symbiont carbon turnover recycled | 0.9 | -- |
| $j_{Xm}$ | Maximum specific feeding rate of host | 0.1292 | molX CmolH^-1^ d^-1^ |
| $K_X$ | Half-saturation constant for prey uptake by host | 20e-6 | molX L^-1^ | 
| $j_{Nm}$ | Maximum specific DIN uptake rate by host | 0.048 | molN CmolH^-1^ d^-1^ |
| $K_N$ | Half-saturation constant for DIN uptake by host | 0.46e-6 | molN L^-1^ | 
| $j_{CO_2}^p$ | Passive CO~2~ delivery to symbiont | 4.04e-3 | molC CmolH^-1^ d^-1^ |
| $j_{CO_2}^a$ | Active CO~2~ delivery to symbiont | 0.32--18.0 | molC CmolH^-1^ d^-1^ |
| $j_{HGm}$ | Maximum specific growth rate of host | 1 | d^-1^ |
| $n_{LC}$ | Quantum yield of photosynthesis | 0.1 | molC mol ph^-1^ |
| $\bar{a}^*$ | Effective light-absorbing cross-section of symbiont | 1.34 | m^2^ CmolS^-1^ |
| $k_{NPQ}$ | NPQ capacity of symbiont, relative to C-fixation | 4 | -- |
| $k_{ROS}$ | Excess photon energy that doubles ROS prod. | 40-80 | mol ph CmolS^-1^ d^-1^ |
| $k$ | Exponent on ROS production rate | 1 | -- |
| $j_{CPm}$ | Maximum specific photosynthesis rate of symbiont | 2.8 | molC CmolS^-1^ d^-1^ |
| $j_{SGm}$ | Maximum specific growth rate of symbiont | 0.25 | d^-1^ |

@@

This excess light energy must be quenched by alternative pathways in order to prevent photo-oxidative damage. *Symbiodinium* may utilize a variety of pathways for non-photochemical quenching [NPQ; @Roth:2014wf], which we collect in a total capacity for NPQ as a parameter of the symbiont ($k_{NPQ}$). If light energy exceeds the total capacity of both carbon fixation and NPQ, then damaging reactive oxygen species (ROS) may be produced. We represent this as a scaled flux of ROS $c_{ROS}$, which takes a value of 1 when all light absorbed is quenched by photochemistry and NPQ, and increases as the amount of excess excitation energy increases.

@@

where $k_{NPQ}$, $k_{ROS}$, and $k$ are parameters of the symbiont that determine the onset and rate of ROS production. Importantly, $c_{ROS}$ as specified here is not a function of absolute light absorption, but rather the amount of excess light energy $j_{eL}$ after accounting for carbon fixation and NPQ. A direct consequence of this formulation is that carbon-limitation of photosynthesis can lead to photo-oxidative stress, a mechanism of biological importance [@Wooldridge:2009p7807] that was not captured by previous representations of photo-oxidative stress [@Eynaud:2011tv]. Moreover, this formulation allows functional diversity among symbiont types to be explored by changing the parameters $k_{NPQ}$, $k_{ROS}$, and $k$.
